Trinity: A Language for Multi-View Architecture Description and Control

### 2017-07-29 sigplanconf-template.tex
Design: Added example arch explanation

\section{Early Design}

>>>>

\section{Design}

	Trinity is designed to unify software architecture design and implementation for not just a single architecture view, but in all three (module, component-and-connector, and deployment).

	To demonstrate how Trinity makes software architecture “live” in Wyvern systems, we have implemented a simple 3-tier web application whose abridged code is shown in Figure 1. In overview, a database is accessed by a server that handles requests from a client. The example architecture contains two components, the client and server. As in more theoretical software architecture, components are runtime entities that may have ports  that act as access points to interact with other components. Our example server and client each have complementary ports, sendInfo and getInfo respectively, that enable interact; here, the server can send information to the client using a JSON connector responsible for serialization and deserialization. Note that Trinity connectors enable the joining two compatible component ports, analogous to ports in software architecture. The architecture’s attachments section actually/physically connects the client and the server using their matching ports and the JSON connector.

	The client and server have their own component-specific architectures given before the general architecture code. Both components have corresponding ports that depend on a client-server interface, denoted by the “requires/provides CSIface” types of each port. This interface is required of a server by the client, as stated by the “requires CSIFace” type, and the server fulfills it, as shown by the “provides CSIface” server port type. The database is an external component of the server, which differs from a component in that the programmer does not provide its source code. “port dbIface: requires DBModule” The database and server are connected by a JDBC connector. This is used within a sub-architecture of the server that connects a specified request handler and the database. Finally, the bindings section of the server’s sub-architecture specifies that the client-facing port, sendInfo, of the server component is indeed the same sendInfo port of the request handler.
